Learning to Infer Graphics Programs from Hand-Drawn Images

### 2018-10-26 nips_2018.tex
long version of the paper
fixed figures

\textbf{Experiment 1: Figure~\ref{syntheticResults}.}
  To evaluate which components of the model are necessary to parse complicated scenes,
  we compared  the neural network
  with SMC against the neural network by
itself (i.e., w/ beam search) or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 12$
objects, it successfully parses scenes with many more objects than the
training data.
We compare with a baseline that produces the spec in one shot by
using the CNN to extract features of the input which are passed to an LSTM which finally predicts
the spec token-by-token (LSTM in Fig.~\ref{syntheticResults}).
This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
but, for this domain, cannot parse cluttered scenes with many objects.
\begin{figure}[h]\centering
  \begin{minipage}[c]{7cm}
      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}    
  \end{minipage}\hspace{0.5cm}%
  \begin{minipage}[c]{6cm}
      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects. Out-of-sample generalization: Model generalizes to scenes with many more objects ($\approx$ at ceiling when tested on twice as many objects as were in the training data). Neither SMC nor the neural network are sufficient on their own. \# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object). Average number of errors is (\# incorrect drawing commands predicted by model)$+$(\# correct commands that were not predicted by model).}\label{syntheticResults}
    \end{minipage}
  \end{figure}
\begin{wrapfigure}{r}{8cm}
  \vspace{-0.2cm}
  \centering

\end{wrapfigure}

@@

\setlength\tabcolsep{3.5pt}
\begin{figure}[H]
  \begin{minipage}[t]{8.25cm}
    \begin{tabular}{llll}
      \includegraphics[width = 2cm]{figures/expert-38.png}&
      \includegraphics[width = 2cm]{figures/expert-73.png}&
      \includegraphics[width = 2cm]{figures/expert-77.png}&
      \includegraphics[width = 2cm]{figures/expert-21.png}
      \\
      \includegraphics[width = 2cm]{figures/38-parse.png}     &
      \includegraphics[width = 2cm]{figures/73-parse.png}     &
      \includegraphics[width = 2cm]{figures/77-parse.png}    &
      \includegraphics[width = 2cm]{figures/21-parse.png}    
      \end{tabular}
    \caption{Left to right: Ising model, recurrent network architecture, figure from a deep learning textbook \cite{Goodfellow-et-al-2016}, graphical model}\label{drawingSuccesses}
  \end{minipage}
\hfill  \begin{minipage}[t]{4.25cm}
    \begin{tabular}{ll}
          \includegraphics[width = 2cm]{figures/expert-1.png}&
          \includegraphics[width = 2cm]{figures/expert-34.png}\\
      \includegraphics[width = 2cm]{figures/expert-1-parse.png}     &
              \includegraphics[width = 2cm]{figures/34-parse.png}    
    \end{tabular}

@@

\begin{table}[t]
  \caption{Drawings (left), their specs (middle left), and programs synthesized from those specs (middle right). Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands. Note the nested loops in second figure, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
%  \vspace{-0.6cm}
\centering  \begin{tabular}{m{1.5cm}llc}
    \toprule
    \textbf{Drawing}&\textbf{Spec}&\textbf{Program}&%\begin{tabular}{c}
      \textbf{Compression factor}%\\\textbf{factor}
      %      \end{tabular}\\
      \\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{lstlisting}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{lstlisting}
for(i<3)
 line(i,-1*i+6,
      2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{lstlisting}
     \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
%%      \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(5,13,2,10,arrow)
%% Circle(5,9)
%% Circle(8,5)
%% Line(2,8, 2,6,arrow)
%% Circle(2,5)
%% \end{lstlisting}
%% \small\emph{... etc. ...; 13 lines}
%% \end{minipage}&
%%              \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
%% circle(4,10)
%% for(i<3)
%%  circle(-3*i+7,5)
%%  circle(-3*i+7,1)
%%  line(-3*i+7,4,-3*i+7,2,arrow)
%%  line(4,9,-3*i+7,6,arrow)
%% \end{lstlisting}
%% \end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
%%     \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Circle(5,8)
%% Circle(2,8)
%% Circle(8,11)
%% Line(2,9, 2,10)
%% Circle(8,8)
%% Line(3,8, 4,8)
%% Line(3,11, 4,11)
%% \end{lstlisting}
%%   \small\emph{... etc. ...; 21 lines}
%% \end{minipage}&\begin{minipage}{\exampleProgramSize}
%% \begin{lstlisting}
%% for(i<3)
%%  for(j<3)
%%   if(j>0)
%%    line(-3*j+8,-3*i+7,
%%         -3*j+9,-3*i+7)
%%    line(-3*i+7,-3*j+8,
%%         -3*i+7,-3*j+9)
%%   circle(-3*j+7,-3*i+7)
%% \end{lstlisting}
%% \end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Rectangle(1,10,3,11)
Rectangle(1,12,3,13)
Rectangle(4,8,6,9)
Rectangle(4,10,6,11)
\end{lstlisting}
  \small\emph{... etc. ...; 16 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<4)
 for(j<4)
  rectangle(-3*i+9,-2*j+6,
            -3*i+11,-2*j+7)
\end{lstlisting}
\end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
%% \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(11,14,13,14,arrow)
%% Circle(10,10)
%% Line(10,13,10,11,arrow)
%% Circle(6,10)
%% \end{lstlisting}
%%     \small\emph{... etc. ...; 15 lines}
%% \end{minipage}&
%% \begin{minipage}{\exampleProgramSize}
%%     \begin{lstlisting}
%% for(i<4)
%%  line(-4*i+13,4,-4*i+13,2,arrow)
%%  for(j<3)
%%   if(j>0)
%%    circle(-4*i+13,4*j+-3)
%%   line(-4*j+10,5,-4*j+12,5,
%%        arrow)
%% \end{lstlisting}
%%   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule

@@

%% \begin{figure}\centering
%%   \begin{tikzpicture}
%%     \node[anchor = west] at (0,5.25) {Entire program search space};
%%     \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
%%     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
%%     \draw [fill = yellow, opacity = 0.4,cycle] (0,5)--(0,1)--(3,5);
%%     \draw [fill = yellow, opacity = 0.6,cycle] (2.5,5)--(3.2,0)--(5,0)--(5,5);
%%     \draw (0,2) -- node[below,sloped]{short programs} (4,0);
%%     \draw (0,2) -- node[above,sloped]{long programs} (4,0);
%%     \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
%%     \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
%%     \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}) = $};
%%     \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
%%     \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}) = $};
%%     \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
%%     \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}) = $};
%%     \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);
%%     \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}) = $};
%%     \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);
%%     \node(p5)[anchor =west ] at ([yshift = -0.5cm]p4.west) {\emph{etc.}};
%%   \end{tikzpicture}
%%   \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs. For example, one subspace might be short programs which don't loop. The policy $\pi$ predicts a distribution over program subspaces. The weight that $\pi$ assigns to a subspace is indicated by it's yellow shading in the above figure.}
%%   \end{figure}
Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
But the actual runtime of the algorithm depends strongly upon
the bias $\probability_{\text{bias}}[\cdot ]$.
Our new approach is to learn $\probability_{\text{bias}}[\cdot ]$
by picking the policy minimizing the
expected bias-optimal time to solve a training corpus, $\mathcal{D}$, of graphics program synthesis problems:
\begin{align}
\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t. }p\text{ evaluates to }S} \text{cost}(p) \nonumber
\end{align}
%Practically, bias optimality has now bought us the following: (1) a guarantee that the policy will always find the minimum cost program; and (2) a differentiable loss function for the policy parameters that takes into account the cost of searching, in contrast to e.g. DeepCoder~\citep{BalGauBroetal16}.

@@

\vspace{1cm}

@@

\pagebreak

@@

\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level image editing.
For example,
we could change all of the circles to squares or make all of the lines be dashed,
or we can (automatically) extrapolate figures
by increasing the number of times that loops are executed.
Extrapolating repetitive visuals patterns comes naturally to humans,
and is a practical application:
imagine hand drawing a repetitive graphical model structure
and having our system automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
\begin{figure}[H]\centering
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix1.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
%  \includegraphics[width = \textwidth]{figures/extrapolationMatrix3.png}  
   \caption{Top, white: drawings. Bottom, black: extrapolations automatically produced by our system.}
  \label{extrapolationFigure}\vspace{-0.25cm}
  \end{figure}
%\input{extrapolations.tex}

@@

We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images using a combination of learning, stochastic search, and program synthesis.
%We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an AI write the code.
More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
\#1753684, and the MUSE program (DARPA grant FA8750-14-2-0242).

>>>>

\textbf{Experiment 1: Figure~\ref{syntheticResults}.}
  To evaluate which components of the model are necessary to parse complicated scenes,
  we compared  the neural network
  with SMC against the neural network by
itself (i.e., w/ beam search) or SMC by itself.  Only the combination of the two passes a
critical test of generalization: when trained on images with $\leq 12$
objects, it successfully parses scenes with many more objects than the
training data.
We compare with a baseline that produces the spec in one shot by
using the CNN to extract features of the input which are passed to an LSTM which finally predicts
the spec token-by-token (LSTM in Fig.~\ref{syntheticResults}).
This architecture is used in several successful neural models of image captioning (e.g.,~\cite{vinyals2015show}),
but, for this domain, cannot parse cluttered scenes with many objects.
\begin{figure}[h]\centering
  \begin{minipage}[c]{7cm}
      \includegraphics[width = 7cm]{figures/averageNumberOfErrors.png}    
  \end{minipage}\hspace{0.5cm}%
  \begin{minipage}[c]{6cm}
      \caption{Parsing~\LaTeX~output after training on diagrams with $\leq 12$ objects. Out-of-sample generalization: Model generalizes to scenes with many more objects ($\approx$ at ceiling when tested on twice as many objects as were in the training data). Neither SMC nor the neural network are sufficient on their own. \# particles varies by model: we compare the models \emph{with equal runtime} ($\approx 1$ sec/object). Average number of errors is (\# incorrect drawing commands predicted by model)$+$(\# correct commands that were not predicted by model).}\label{syntheticResults}
    \end{minipage}
  \end{figure}

@@

\setlength\tabcolsep{3.5pt}
\begin{figure}[H]
  \begin{minipage}[t]{9cm}
    \begin{tabular}{llll}
      \includegraphics[width = 2cm]{figures/expert-38.png}&
      \includegraphics[width = 2cm]{figures/expert-73.png}&
      \includegraphics[width = 2cm]{figures/expert-77.png}&
      \includegraphics[width = 2cm]{figures/expert-21.png}
      \\
      \includegraphics[width = 2cm]{figures/38-parse.png}     &
      \includegraphics[width = 2cm]{figures/73-parse.png}     &
      \includegraphics[width = 2cm]{figures/77-parse.png}    &
      \includegraphics[width = 2cm]{figures/21-parse.png}    
      \end{tabular}
    \caption{Left to right: Ising model, recurrent network architecture, figure from a deep learning textbook \cite{Goodfellow-et-al-2016}, graphical model}\label{drawingSuccesses}
  \end{minipage}
\hfill  \begin{minipage}[t]{4.25cm}
    \begin{tabular}{ll}
          \includegraphics[width = 2cm]{figures/expert-1.png}&
          \includegraphics[width = 2cm]{figures/expert-34.png}\\
      \includegraphics[width = 2cm]{figures/expert-1-parse.png}     &
              \includegraphics[width = 2cm]{figures/34-parse.png}    
    \end{tabular}

@@

\begin{table}[t]
  \caption{Drawings (left), their specs (middle left), and programs synthesized from those specs (middle right). Compared to the specs the programs are more compressive (right: programs have fewer lines than specs) and automatically group together related drawing commands. Note the nested loops  and conditionals in the Ising model, combination of symmetry and iteration in the bottom figure,  affine transformations in the top figure, and the complicated program in the second figure to bottom.}\label{exampleSynthesisResults}
%  \vspace{-0.6cm}
\centering  \begin{tabular}{m{1.5cm}llc}
    \toprule
    \textbf{Drawing}&\textbf{Spec}&\textbf{Program}&%\begin{tabular}{c}
      \textbf{Compression factor}%\\\textbf{factor}
      %      \end{tabular}\\
      \\
    \midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-29-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(2,15, 4,15)
Line(4,9, 4,13)
Line(3,11, 3,14)
Line(2,13, 2,15)
Line(3,14, 6,14)
Line(4,13, 8,13)
\end{lstlisting}
\end{minipage}&     \begin{minipage}{\exampleProgramSize} \begin{lstlisting}
for(i<3)
 line(i,-1*i+6,
      2*i+2,-1*i+6)
 line(i,-2*i+4,i,-1*i+6)
       \end{lstlisting}
     \end{minipage}&$\frac{6}{3} = 2\text{x}$\\\midrule
     \includegraphics[width = \exampleDrawingSize]{figures/expert-52-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Line(5,13,2,10,arrow)
Circle(5,9)
Circle(8,5)
Line(2,8, 2,6,arrow)
Circle(2,5)
\end{lstlisting}
\small\emph{... etc. ...; 13 lines}
\end{minipage}&
             \begin{minipage}{\exampleProgramSize}\begin{lstlisting}
circle(4,10)
for(i<3)
 circle(-3*i+7,5)
 circle(-3*i+7,1)
 line(-3*i+7,4,-3*i+7,2,arrow)
 line(4,9,-3*i+7,6,arrow)
\end{lstlisting}
\end{minipage}&$\frac{13}{6} = 2.2\text{x}$\\\midrule
    \includegraphics[width = \exampleDrawingSize]{figures/expert-38-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Circle(5,8)
Circle(2,8)
Circle(8,11)
Line(2,9, 2,10)
Circle(8,8)
Line(3,8, 4,8)
Line(3,11, 4,11)
\end{lstlisting}
  \small\emph{... etc. ...; 21 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<3)
 for(j<3)
  if(j>0)
   line(-3*j+8,-3*i+7,
        -3*j+9,-3*i+7)
   line(-3*i+7,-3*j+8,
        -3*i+7,-3*j+9)
  circle(-3*j+7,-3*i+7)
\end{lstlisting}
\end{minipage}&$\frac{21}{6} = 3.5\text{x}$\\\midrule
\includegraphics[width = \exampleDrawingSize]{figures/expert-101-trim.png}&
\begin{minipage}{\exampleTraceSize}\begin{lstlisting}
Rectangle(1,10,3,11)
Rectangle(1,12,3,13)
Rectangle(4,8,6,9)
Rectangle(4,10,6,11)
\end{lstlisting}
  \small\emph{... etc. ...; 16 lines}
\end{minipage}&\begin{minipage}{\exampleProgramSize}
\begin{lstlisting}
for(i<4)
 for(j<4)
  rectangle(-3*i+9,-2*j+6,
            -3*i+11,-2*j+7)
\end{lstlisting}
\end{minipage}&$\frac{16}{3} = 5.3\text{x}$\\\midrule
%% \includegraphics[width = \exampleDrawingSize]{figures/expert-75-extra-trim.png}&
%% \begin{minipage}{\exampleTraceSize}\begin{lstlisting}
%% Line(11,14,13,14,arrow)
%% Circle(10,10)
%% Line(10,13,10,11,arrow)
%% Circle(6,10)
%% \end{lstlisting}
%%     \small\emph{... etc. ...; 15 lines}
%% \end{minipage}&
%% \begin{minipage}{\exampleProgramSize}
%%     \begin{lstlisting}
%% for(i<4)
%%  line(-4*i+13,4,-4*i+13,2,arrow)
%%  for(j<3)
%%   if(j>0)
%%    circle(-4*i+13,4*j+-3)
%%   line(-4*j+10,5,-4*j+12,5,
%%        arrow)
%% \end{lstlisting}
%%   \end{minipage}&$\frac{15}{6} = 2.5\text{x}$\\\midrule

@@

%% \begin{figure}\centering
%%   \begin{minipage}[c]{0.4\textwidth}
%%     \begin{tikzpicture}[scale=0.8]
%%         \node[anchor = west] at (0,5.25) {Entire program search space};
%%         \footnotesize
%%     \draw[fill = yellow,fill opacity = 0.15,draw = black] (0,0) rectangle (5,5);
%%     \draw [fill = yellow, opacity = 0.2] (0,0)--(0,2)--(4,0)--(0,0);
%%     \draw [fill = yellow, opacity = 0.4] (0,5)--(0,1)--(3,5);
%%     \draw [fill = yellow, opacity = 0.6] (2.5,5)--(3.2,0)--(5,0)--(5,5);
%%     \draw (0,2) -- node[below,sloped]{short programs} (4,0);
%%     \draw (0,2) -- node[above,sloped]{long programs} (4,0);
%%     \draw (2.5,5) -- node[above,sloped]{programs w/ reflections} (3.2,0);
%%     \draw (0,1) -- node[above,sloped]{ programs w/ loops} (3,5);
%%     %% \node(p1)[anchor =west ] at (5.5,3.5) {$\pi_\theta(\text{short, no loop/reflect}|S) = $};
%%     %% \draw [fill = yellow, fill opacity = 0.2,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p1.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p1.east);
%%     %    \node(p2)[anchor =west ] at ([yshift = -0.5cm]p1.west) {$\pi_\theta(\text{long, loops}|S) = $};

%%     %% \node(p2)[anchor =west ] at (0,-0.5) {$\pi_\theta(\text{long, loops}|S) = $};
%%     %% \draw [fill = yellow, fill opacity = 0.4,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p2.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p2.east);
%%     %% \node(p3)[anchor =west ] at ([yshift = -0.5cm]p2.west) {$\pi_\theta(\text{long, no loop/reflect}|S) = $};
%%     %% \draw [fill = yellow, fill opacity = 0.15,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p3.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p3.east);

%%     %% \node(p4)[anchor =west ] at ([yshift = -0.5cm]p3.west) {$\pi_\theta(\text{long, reflects}|S) = $};
%%     %% \draw [fill = yellow, fill opacity = 0.6,draw = black]  ([xshift = 0cm,yshift = -0.2cm]p4.east) rectangle ([xshift = 0.4cm,yshift = 0.2cm]p4.east);

%%     %\node(p5)[anchor =west ] at ([yshift = -0.5cm]p3.west) {\emph{etc.}};
%%   \end{tikzpicture}
%%     \end{minipage}
%%   \begin{minipage}[c]{0.5\textwidth}
%%           \caption{The bias-optimal search algorithm divides the entire (intractable) program search space in to (tractable) program subspaces (written $\sigma $), each of which contains a restricted set of programs. For example, one subspace might be short programs which don't loop. The policy $\pi$ predicts a distribution over program subspaces. The weight that $\pi$ assigns to a subspace is indicated by its yellow shading in the above figure, and is conditioned on the spec $S$.}
%%     \end{minipage}
%%   \end{figure}

Now in theory any $\pi_\theta(\cdot |\cdot ) $ is a bias-optimal searcher.
But the actual runtime of the algorithm depends strongly upon
the bias $\probability_{\text{bias}}[\cdot ]$.
Our new approach is to learn $\probability_{\text{bias}}[\cdot ]$
by picking the policy minimizing the
expected bias-optimal time to solve a training corpus, $\mathcal{D}$, of graphics program synthesis problems:
\begin{align}
\textsc{Loss}(\theta ; \mathcal{D})& =  \expect_{S\sim\mathcal{D}}\left[ \min_{\sigma\in \text{\textsc{Best}}(S)}\frac{t(\sigma | S)}{\pi_\theta (\sigma | S)}\right] + \lambda \Vert\theta\Vert_2^2\label{policyLoss}\\
\text{where }  \sigma \in\text{\textsc{Best}}(S) &\text{ if  a minimum cost program for }S \text{ is in }\sigma .\nonumber %\text{cost}(\text{program}(p)) = \min_{p\in \sigma \text{, s.t. }p\text{ evaluates to }S} \text{cost}(p) \nonumber
\end{align}
%Practically, bias optimality has now bought us the following: (1) a guarantee that the policy will always find the minimum cost program; and (2) a differentiable loss function for the policy parameters that takes into account the cost of searching, in contrast to e.g. DeepCoder~\citep{BalGauBroetal16}.

@@

\vspace{0.2cm}

@@

@@

\subsection{Extrapolating figures}
Having access to the source code of a graphics program facilitates coherent, high-level image editing.
For example,
we could change all of the circles to squares or make all of the lines be dashed,
or we can (automatically) extrapolate figures
by increasing the number of times that loops are executed.
Extrapolating repetitive visuals patterns comes naturally to humans,
and is a practical application:
imagine hand drawing a repetitive graphical model structure
and having our system automatically induce and extend the pattern.
Fig.~\ref{extrapolationFigure} shows extrapolations produced by our system.
\begin{figure}[H]\centering
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix1.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix2.png}
  \includegraphics[width = 0.885\textwidth]{figures/extrapolationMatrix3.png}  
   \caption{Top, white: drawings. Bottom, black: extrapolations automatically produced by our system.}
  \label{extrapolationFigure}\vspace{-0.5cm}
  \end{figure}
%\input{extrapolations.tex}

@@

We have presented a system for inferring graphics programs which generate \LaTeX-style figures from hand-drawn images using a combination of learning, stochastic search, and program synthesis.
%We evaluated our model's performance at parsing novel images, and we demonstrated its ability to extrapolate from provided drawings.
In the near future, we believe it will be possible to produce professional-looking figures just by drawing them and then letting an AI write the code.
More generally, we believe the problem of inferring visual programs is a promising direction for research in machine perception.
\subsubsection*{Acknowledgments} We are grateful for advice from Will Grathwohl and Jiajun Wu on  the neural architecture. Funding from NSF GRFP, NSF Award 
\#1753684, the MUSE program (DARPA grant FA8750-14-2-0242),
and AFOSR award FA9550-16-1-0012.
